An Open Platform for Managing Short Programming Exercises

### 2013-06-18 paper/paper.tex
change address
de-anonymize links
better example screenshot

\author{
\alignauthor
Andrei Papancea\\
Jaime Spacco\\
       \affaddr{Department of Computer Science}\\
       \affaddr{Knox College}\\
       \affaddr{Galesburg, IL 61401}\\
       \email{\{apapance,jspacco\}@knox.edu}
% 2nd. author
\alignauthor
David Hovemeyer\\
       \affaddr{Kinsley Engineering Center}\\
       \affaddr{York College of Pennsylvania}\\
       \affaddr{York, PA 17403}\\
       \email{dhovemey@ycp.edu}
}

@@

\begin{figure*}[ht]
\centering
\includegraphics[width=180mm]{images/screenshot}
\caption{Screenshot of the main view in CloudCoder.}
\label{screenshot}
\end{figure*}

CloudCoder is available under the GNU Affero open-source license.
Binary distributions are available through our website (anonymized),
and the code is available on Github:

\vspace*{3mm} 
%\url{https://github.com/cloudcoderdotorg/CloudCoder}
(link anonymized)
\vspace*{3mm}

@@

\vspace*{3mm} 
% \url{https://cloudcoder.org/repo}
(link anonymized)
\vspace*{3mm}

>>>>

\author{
\alignauthor
Andrei Papancea\\
Jaime Spacco\\
       \affaddr{Department of Computer Science}\\
       \affaddr{Knox College}\\
       \affaddr{Galesburg, IL 61401}\\
       \email{\{apapance,jspacco\}@knox.edu}
% 2nd. author
\alignauthor
David Hovemeyer\\
       \affaddr{Department of Physical Sciences}\\
       \affaddr{York College of Pennsylvania}\\
       \affaddr{York, PA 17403}\\
       \email{dhovemey@ycp.edu}
}

@@

\begin{figure*}[ht]
\centering
\includegraphics[width=5.5in]{images/screenshot4}
\caption{Screenshot of the main view in CloudCoder}
\label{screenshot}
\end{figure*}

CloudCoder is available under the GNU Affero open-source license.
Binary distributions are available through our website (\url{http://cloudcoder.org}),
and the code is available on Github:

\vspace*{3mm} 
\url{https://github.com/cloudcoderdotorg/CloudCoder}
\vspace*{3mm}

@@

\vspace*{3mm} 
\url{https://cloudcoder.org/repo}
\vspace*{3mm}
